Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)

### 2021-09-24 docs/updated_manuscript/updated_manuscript.Rmd
updated version of preprint with sixth article

---
title             : "Data irregularities across five implicit learning articles: Comments on @lola2021, @lola2020, @tzetzis2015, @lola2012, and @tzetzis2010"

@@

abstract: |
  We present a critical re-analysis of five implicit learning papers published by the same authors between 2010 and 2021. We calculated effect sizes for each pairwise comparison reported in the papers using the data published in each article. We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations. We found the pairwise effect sizes were implausible in all five articles in question, with Cohen’s *d* values often exceeding 100 and sometimes exceeding 1000. Impossible statistics were reported in four out of the five articles. Reported test statistics and $\eta^{2}$ values were also implausible, with several $\eta^{2}$ = .99 and even $\eta^{2}$ = 1.0 for between-subjects main effects. The results reported in the five articles in question are unreliable. Many of the problems we identified could be spotted without further analysis, highlighting the need for adequate statistical training in the field of motor learning.

@@

Statistical reporting errors may commonly occur in psychology articles [@brown2017; @nuijten2016] and such errors are often consistent with hypothesized results [@bakker2011]. When the primary conclusions in research articles depend on reporting errors, replicability is unlikely and future research may be wasted if researchers attempt to build on the erroneously reported results [@munafo2017]. In this paper, we scrutinize five papers published by the same two authors[^1], where the authors report a high number of erroneous or implausible data on which their primary conclusions depend. We first became aware of the @lola2021 paper when the paper was highlighted in a social media post [@gray2021]. During an initial read through by one of us (BM), a number of reporting and/or statistical issues were noticed. The paper also referenced past research published by these authors. Given our cause for concern over the issues found in the @lola2021 paper, we deemed it necessary to examine these other papers. We remain agnostic to the sources of error in each of these papers. Nevertheless, the data irregularities we found are similar across the target articles and at times even include repeated values (e.g., $F$-statistics) across multiple papers. Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions. Below, we outline our causes for concern and the overarching issues we found across the five articles in question.

[^1]: One of the five papers had a third author.

@@

We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague [@lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015]. All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \@ref(tab:table1)). In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills. Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics. We will refer to the five articles throughout this paper using the following numbering system:

@@

2.  Lola, A.C., & Tzetzis, G.C. (2020). Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy. *Journal of Physical Education and Sport*, 20(5), 2478-2486. https://doi.org/10.7752/jpes.2020.05339

3.  Tzetzis, G.C., & Lola, A.C. (2015). The effect of analogy, implicit, and explicit learning on anticipation in volleyball serving. *International Journal of Sport Psychology*, 46(2), 152-166. https://doi.org/10.7352/IJSP.2015.46.152

4.  Lola, A.C., & Tzetzis, G.C., & Zetou, H. (2012). The effect of implicit and explicit practice in the development of decision making in volleyball serving. *Perceptual and Motor Skills*, 114(2), 665-678. https://doi.org/10.2466/05.23.25.PMS.114.2.665-678

5.  Tzetzis, G.C., & Lola, C.A. (2010). The role of implicit, explicit instruction and their combination in learning anticipation skill, under normal and stress conditions. *International Journal of Sport Sciences and Physical Education*, 1, 54-59.[^2]

[^2]: This article is in a journal of a publishing group that has been identified as a potential predatory journal. Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS). In fact, the earliest available issue on the journal's webpage is from 2016.

@@

table_1 <- tibble::tibble(
  c1 = c("Lola \\& Tzetzis (2021)",
         "Lola \\& Tzetzis (2020)",
         "Tzetzis \\& Lola (2015)",
         "Lola et al (2012)",
         "Tzetzis \\& Lola (2010)"),
  c2 = c("60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
         "80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
         "60 females, age range: 9 to 12 years ($M_{age}$ = 10.48, SD = 0.91)\\textsuperscript{a}",
         "60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)",
         "48 females, age range: 12 to 13 years ($M_{age}$ = 12.38, SD = 0.34)")
)

kbl(table_1,
    booktabs = TRUE,
    escape = FALSE,
    caption = "Participant demographics in each of the target articles.",
    col.names = c("Target article",
                  "Sample size and participant details"),
    align = c("l", "l")) %>%
  kable_styling(position = "left",
                font_size = 11) %>%
  pack_rows("Article 1", 1, 1) %>%
  pack_rows("Article 2", 2, 2) %>%
  pack_rows("Article 3", 3, 3) %>%
  pack_rows("Article 4", 4, 4) %>%
  pack_rows("Article 5", 5, 5) %>%
  footnote(alphabet = c("Articles 1-3 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2."),
           alphabet_title = "Note.",
           threeparttable = TRUE)

@@

Although there were some differences between the reported experiments in the target articles, there were many methodological commonalities that can be summarized. All five articles involved female children learning a volleyball skill as part of a volleyball camp. In each case, the participants were reported to have minimal experience (i.e., were described as novices) with the task at hand. The purpose of all five experiments was to evaluate perceptual or motor learning differences as a function of the type of instruction received during practice. Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test. The authors also included a high stress test in Articles 1 and 5.

In Articles 1-3, the groups differed with respect to the type of instruction received: implicit, explicit, or analogy. In Articles 4 and 5, a sequential group (see below for description) replaced the analogy group. All five experiments also included a control group that did not practice the task. Implicit instruction did not contain any explicit information for how to perform the task and the learners were asked to perform a distracting task like counting backwards while practicing to prevent them from acquiring declarative rules for performance. In contrast, explicit instruction consisted of direct verbal instructions for performing the task. Analogy instruction was considered a type of implicit instruction wherein an analogy or metaphor was provided to the learner. For example, "Imagine that the opponents' surface is covered with water. Send the ball where there is more water and no opponents at the court." [@lola2021, p. 9]. Sequential instruction involved receiving explicit instruction for the first half of training followed by implicit instruction for the second half of training. Across experiments, the authors predicted that implicit forms of instruction---implicit, analogy, and sequential---would be more effective than explicit instruction for motor and perceptual learning. This advantage was also predicted to be greater when testing was conducted in a high stress situation. In @lola2021 for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team. Further, it was predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.

The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2). In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 2 had a measure of self-efficacy using a Likert scale. Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.

@@

None of the five articles in question included a link to a public repository where the data could be accessed. We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment. The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A. Lola, personal communication, February 12 2021). We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2-5 as these articles were less recent and presumably, all planned analyses had been completed. After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2-5. The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A. Lola, personal communication, March 2 2021).

Our first two requests did not include any indication about our concerns regarding the data irregularities. Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article and once again reiterated our request to the authors to share any available data for any of the target articles. These requests were once again refused. The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns. Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles. The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles. Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A. Lola, personal communication, April 22 2021). We illustrate below that the data *and* analyses reported in each of the articles reviewed are unreliable. Our extracted data and analysis scripts can be accessed at the following link: https://osf.io/raz6q/.

@@

Means and standard deviations were extracted from each article for all measures and time points that were reported. Cohen's *d* was calculated for each pairwise comparison using the `compute.es` package in `R`. To provide context, we simulated data from two groups of *n* = 20, consistent with groups sizes in Articles 1-4. We ran simulations with true effect sizes of *d* = .8 and *d* = 3 one million times each and report the range of effect sizes observed in those simulations.

@@

To evaluate the maximum range of plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)). We set the true effect size at *d* = .8, the conventional benchmark for a "large" treatment effect, in the first simulation. The largest effect size observed from the one million simulated experiments was *d* = 2.97. In the second simulation, we set the true effect size at *d* = 3, an unrealistically large effect size that might rarely be encountered in the psychology and/or motor learning literature. The maximum effect size observed in the one million simulated experiments was *d* = 6.6.

(ref:fig1-caption) Absolute Cohen's $d$ estimates from Articles 1-4 plotted on a logarithmic scale. All pairwise comparisons have been included for all dependent measures in each experiment. The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = .8 is illustrated by shaded green and blue regions of the figure, reaching a maximum value of $d$ = 2.97. The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = 3 is illustrated by the shaded purple and blue regions of the figure, reaching a maximum value of $d$ = 6.6.

@@

In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes. In Article 1, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article. The smallest post-intervention effect at any of the three time points was *d* = 286.42, while the largest effect was *d* = 3504.86. A similar picture emerges when analyzing the accuracy data. All the pre-test differences were improbably large (all *d*'s $\geq$ 2.52) despite being reported as not significantly different in the articles. Ten of the pairwise comparisons resulted in *d*'s $\geq$ 100 following treatment with the independent variables. The motor component data revealed post-treatment effect sizes ranging from *d* = 1.16 to *d* = 13.5.

In Article 2, post-intervention motor performance effect sizes ranged from *d* = 3.1 to *d* = 20.95. Similarly, post-intervention self-efficacy effect sizes ranged from *d* = 1.79 to *d* = 44.46. Likewise, in Article 3 post-intervention reaction time effect sizes ranged from *d* = 2.28 to *d* = 35.97. Continuing this pattern, post-intervention response accuracy effect sizes ranged from *d* = 5.84 to *d* = 29.7.

In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from *d* = 2.53 to *d* = 15.50. Nevertheless, all pre-test comparisons were reported as non-significant. Following intervention, the effect sizes ranged from *d* = 23.13 to *d* = 155.08. Relative to other reported effect sizes, those reported for reaction time were not implausibly large at any time point, ranging from *d* = 0 to *d* = .86. However, the authors reported an implausibly large effect size, $\eta^{2}$ = .94, for the 4 (Group) x 3 (Time) ANOVA. Further, despite only one pairwise comparison being statistically significant, all post-intervention comparisons were reported as being significant in the article.

In Article 5, the authors did not report means and standard deviations for most of the analyses. However, $\eta^{2}$ effect sizes were reported and these ranged from $\eta^{2}$ = .52 to $\eta^{2}$ = .98. These effect sizes are discussed further below. All the post-intervention effects reviewed above were directionally consistent with the researchers' expectations. The sometimes implausibly large pre-test effects were not expected, but also were not reported as significant.

@@

In Article 2, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles. Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.[^3] Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09. The perfect score was not a rounding error because the same group was reported to have a mean score of 2.99 with a standard deviation of .11 on the post-test. These data are not possible.

[^3]: Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task [see @fischman2015; @hancock1995; @reeve1994 for discussions].

Articles 1, 4, and 5 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase. As a single item analysis of integers these results were suitable for a GRIMMER analysis. In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups. In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78). The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent. In Article 5, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample. For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used. However, the results for the explicit group were GRIMMER inconsistent (*M* = 4.8, *SD* = 1.78).[^4]

[^4]: You may have noticed that the same mean and standard deviation pairing (*M* = 4.8, *SD* = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other. This is because of sample size differences (*n* = 20 for the consistent result and *n* = 12 for the inconsistent one).

@@

Article 1 did not report $\eta^{2}$ values but had the largest pairwise effects and *F*-statistics of the five articles in question. Article 2 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance, respectively. Similarly, variance explained on the self-efficacy measure was $\eta^{2}$ = .995, $\eta^{2}$ = .994, $\eta^{2}$ = .997 for the Time, Group, and Time x Group effects, respectively. Article 3 also reported $\eta^{2}$ = .99 for all three effects on both response time and response accuracy measures.

Article 4 reported $\eta^{2}$ = 1.0 for the main effect of Time and the Time x Group interaction, as well as $\eta^{2}$ = .95 for the main effect of Group on the response time measure. Interestingly, the Time x Group interaction had the smallest reported significant *F*-statistic among the five articles in question. With respect to response accuracy, the reported effects were $\eta^{2}$ = .98, $\eta^{2}$ = .94, $\eta^{2}$ = .93 for the Time, Group, and Time x Group analyses, respectively. Article 5 reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses, respectively.

@@

Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 3, 4, and 5. The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4). Articles 1-3 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 3, and 80 in Article 2. Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \@ref(tab:table1)). We assumed that each article was based on different samples as none of the articles mentioned using any previously published data.

>>>>

---
title             : "Data irregularities across six implicit learning articles: Comments on @lola2021, @lola2021b, @lola2020, @tzetzis2015, @lola2012, and @tzetzis2010"

@@

abstract: |
  We present a critical re-analysis of six implicit learning papers published by the same authors between 2010 and 2021. We calculated effect sizes for each pairwise comparison reported in the papers using the data published in each article. We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations. We found the pairwise effect sizes were implausible in all six articles in question, with Cohen’s *d* values often exceeding 100 and sometimes exceeding 1000. Impossible statistics were reported in four out of the six articles. Reported test statistics and $\eta^{2}$ values were also implausible, with several $\eta^{2}$ = .99 and even $\eta^{2}$ = 1.0 for between-subjects main effects. The results reported in the six articles in question are unreliable. Many of the problems we identified could be spotted without further analysis, highlighting the need for adequate statistical training in the field of motor learning.

@@

Statistical reporting errors may commonly occur in psychology articles [@brown2017; @nuijten2016] and such errors are often consistent with hypothesized results [@bakker2011]. When the primary conclusions in research articles depend on reporting errors, replicability is unlikely and future research may be wasted if researchers attempt to build on the erroneously reported results [@munafo2017]. In this paper, we scrutinize six papers published by the same two authors[^1], where the authors report a high number of erroneous or implausible data on which their primary conclusions depend. We first became aware of the @lola2021 paper when the paper was highlighted in a social media post [@gray2021]. During an initial read through by one of us (BM), a number of reporting and/or statistical issues were noticed. The paper also referenced past research published by these authors. Given our cause for concern over the issues found in the @lola2021 paper, we deemed it necessary to examine these other papers. We remain agnostic to the sources of error in each of these papers. Nevertheless, the data irregularities we found are similar across the target articles and at times even include repeated values (e.g., $F$-statistics) across multiple papers. Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions[^2]. Below, we outline our causes for concern and the overarching issues we found across the six articles in question.

[^1]: One of the six papers had a third author and one had a third and fourth author.
[^2]: After sharing a preprint of the original version of this paper, the editors of the *International Journal of Sport and Exercise Psychology* have indicated they intend to retract @lola2021.

@@

We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague [@lola2012; @lola2020; @lola2021; @lola2021b; @tzetzis2010; @tzetzis2015]. All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \@ref(tab:table1)). In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills. Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics. We will refer to the six articles throughout this paper using the following numbering system:

@@

2. Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., & Tzetzis, G.C. (2021). The influence of analogies on the development of selective attention in novices in normal or stressful conditions. *Journal of Human Sport and Exercise, in press*. https://doi.org/10.14198/jhse.2023.181.12

3.  Lola, A.C., & Tzetzis, G.C. (2020). Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy. *Journal of Physical Education and Sport*, 20(5), 2478-2486. https://doi.org/10.7752/jpes.2020.05339

4.  Tzetzis, G.C., & Lola, A.C. (2015). The effect of analogy, implicit, and explicit learning on anticipation in volleyball serving. *International Journal of Sport Psychology*, 46(2), 152-166. https://doi.org/10.7352/IJSP.2015.46.152

5.  Lola, A.C., & Tzetzis, G.C., & Zetou, H. (2012). The effect of implicit and explicit practice in the development of decision making in volleyball serving. *Perceptual and Motor Skills*, 114(2), 665-678. https://doi.org/10.2466/05.23.25.PMS.114.2.665-678

6.  Tzetzis, G.C., & Lola, C.A. (2010). The role of implicit, explicit instruction and their combination in learning anticipation skill, under normal and stress conditions. *International Journal of Sport Sciences and Physical Education*, 1, 54-59.[^3]

[^3]: This article is in a journal of a publishing group that has been identified as a potential predatory journal. Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS). In fact, the earliest available issue on the journal's webpage is from 2016.

@@

table_1 <- tibble::tibble(
  c1 = c("Lola \\& Tzetzis (2021)",
         "Lola et al (2021)",
         "Lola \\& Tzetzis (2020)",
         "Tzetzis \\& Lola (2015)",
         "Lola et al (2012)",
         "Tzetzis \\& Lola (2010)"),
  c2 = c("60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
         "60 females, age range: 11 to 12 years (mean and standard deviation not reported)",
         "80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
         "60 females, age range: 9 to 12 years ($M_{age}$ = 10.48, SD = 0.91)\\textsuperscript{a}",
         "60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)",
         "48 females, age range: 12 to 13 years ($M_{age}$ = 12.38, SD = 0.34)")
)

kbl(table_1,
    booktabs = TRUE,
    escape = FALSE,
    caption = "Participant demographics in each of the target articles.",
    col.names = c("Target article",
                  "Sample size and participant details"),
    align = c("l", "l")) %>%
  kable_styling(position = "left",
                font_size = 11) %>%
  pack_rows("Article 1", 1, 1) %>%
  pack_rows("Article 2", 2, 2) %>%
  pack_rows("Article 3", 3, 3) %>%
  pack_rows("Article 4", 4, 4) %>%
  pack_rows("Article 5", 5, 5) %>%
  pack_rows("Article 6", 6, 6) %>%
  footnote(alphabet = c("Articles 1,3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2."),
           alphabet_title = "Note.",
           threeparttable = TRUE)

@@

Although there were some differences between the reported experiments in the target articles, there were many methodological commonalities that can be summarized. All six articles involved female children learning a volleyball skill as part of a volleyball camp. In each case, the participants were reported to have minimal experience (i.e., were described as novices) with the task at hand. The purpose of all six experiments was to evaluate perceptual or motor learning differences as a function of the type of instruction received during practice. Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test. The authors also included a high stress test in Articles 1, 2 and 6.

In Articles 1-4, the groups differed with respect to the type of instruction received: implicit, explicit, or analogy. In Articles 5 and 6, a sequential group (see below for description) replaced the analogy group. All six experiments also included a control group that did not practice the task. Implicit instruction did not contain any explicit information for how to perform the task and the learners were asked to perform a distracting task like counting backwards while practicing to prevent them from acquiring declarative rules for performance. In contrast, explicit instruction consisted of direct verbal instructions for performing the task. Analogy instruction was considered a type of implicit instruction wherein an analogy or metaphor was provided to the learner. For example, "Imagine that the opponents' surface is covered with water. Send the ball where there is more water and no opponents at the court." [@lola2021, p. 9]. Sequential instruction involved receiving explicit instruction for the first half of training followed by implicit instruction for the second half of training. Across experiments, the authors predicted that implicit forms of instruction---implicit, analogy, and sequential---would be more effective than explicit instruction for motor and perceptual learning. This advantage was also predicted to be greater when testing was conducted in a high stress situation. In @lola2021 for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team. Further, it was predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.

The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3). In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 3 had a measure of self-efficacy using a Likert scale. Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.

@@

None of the six articles in question included a link to a public repository where the data could be accessed. We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment. The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A. Lola, personal communication, February 12 2021). We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent and presumably, all planned analyses had been completed. After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 3-6. The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A. Lola, personal communication, March 2 2021).

Our first two requests did not include any indication about our concerns regarding the data irregularities. Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article (except @lola2021b, which was not published yet) and once again reiterated our request to the authors to share any available data for any of the target articles. These requests were once again refused. The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns. Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles. The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles. Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A. Lola, personal communication, April 22 2021). We illustrate below that the data *and* analyses reported in each of the articles reviewed are unreliable. Our extracted data and analysis scripts can be accessed at the following link: https://osf.io/raz6q/.

@@

Means and standard deviations were extracted from each article for all measures and time points that were reported. Cohen's *d* was calculated for each pairwise comparison using the `compute.es` package in `R`. To provide context, we simulated data from two groups of *n* = 20, consistent with group sizes in Article 3, which had the largest groups among the target articles. We ran simulations with true effect sizes of *d* = .8 and *d* = 3 one million times each and report the range of effect sizes observed in those simulations.

@@

To evaluate the maximum range of plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)). We set the true effect size at *d* = .8, the conventional benchmark for a "large" treatment effect, in the first simulation. The largest effect size observed from the one million simulated experiments was *d* = 2.97. In the second simulation, we set the true effect size at *d* = 3, an unrealistically large effect size that might rarely be encountered in the psychology and/or motor learning literature. The maximum effect size observed in the one million simulated experiments was *d* = 6.6.

(ref:fig1-caption) Absolute Cohen's $d$ estimates from Articles 1-5 plotted on a logarithmic scale. All pairwise comparisons have been included for all dependent measures in each experiment. The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = .8 is illustrated by shaded green and blue regions of the figure, reaching a maximum value of $d$ = 2.97. The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = 3 is illustrated by the shaded purple and blue regions of the figure, reaching a maximum value of $d$ = 6.6.

@@

In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes. In Article 1, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article. The smallest post-intervention effect at any of the three time points was *d* = 286.42, while the largest effect was *d* = 3504.86. A similar picture emerges when analyzing the accuracy data. All the pre-test differences were improbably large (all *d*'s $\geq$ 2.52) despite being reported as not significantly different in the articles. Ten of the pairwise comparisons resulted in *d*'s $\geq$ 100 following treatment with the independent variables. The motor component data revealed post-treatment effect sizes ranging from *d* = 1.16 to *d* = 13.5.

In Article 2, the smallest post-intervention difference in reaction times was *d* = .64. However, all other effects were larger than *d* = 8.7 and the largest effect was *d* = 41.0. The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger *d* = 5.0 and a largest effect of *d* = 13.35.

In Article 3, post-intervention motor performance effect sizes ranged from *d* = 3.1 to *d* = 20.95. Similarly, post-intervention self-efficacy effect sizes ranged from *d* = 1.79 to *d* = 44.46. Likewise, in Article 4 post-intervention reaction time effect sizes ranged from *d* = 2.28 to *d* = 35.97. Continuing this pattern, post-intervention response accuracy effect sizes ranged from *d* = 5.84 to *d* = 29.7.

In Article 5, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from *d* = 2.53 to *d* = 15.50. Nevertheless, all pre-test comparisons were reported as non-significant. Following intervention, the effect sizes ranged from *d* = 23.13 to *d* = 155.08. Relative to other reported effect sizes, those reported for reaction time were not implausibly large at any time point, ranging from *d* = 0 to *d* = .86. However, the authors reported an implausibly large effect size, $\eta^{2}$ = .94, for the 4 (Group) x 3 (Time) ANOVA. Further, despite only one pairwise comparison being statistically significant, all post-intervention comparisons were reported as being significant in the article.

In Article 6, the authors did not report means and standard deviations for most of the analyses. However, $\eta^{2}$ effect sizes were reported and these ranged from $\eta^{2}$ = .52 to $\eta^{2}$ = .98. These effect sizes are discussed further below. All the post-intervention effects reviewed above were directionally consistent with the researchers' expectations. The sometimes implausibly large pre-test effects were not expected, but also were not reported as significant.

@@

In Article 3, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles. Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.[^4] Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09. The perfect score was not a rounding error because the same group was reported to have a mean score of 2.99 with a standard deviation of .11 on the post-test. These data are not possible.

[^4]: Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task [see @fischman2015; @hancock1995; @reeve1994 for discussions].

Articles 1, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase. As a single item analysis of integers these results were suitable for a GRIMMER analysis. In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups. In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78). The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent. In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample. For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used. However, the results for the explicit group were GRIMMER inconsistent (*M* = 4.8, *SD* = 1.78).[^5]

[^5]: You may have noticed that the same mean and standard deviation pairing (*M* = 4.8, *SD* = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other. This is because of sample size differences (*n* = 20 for the consistent result and *n* = 12 for the inconsistent one).

@@

Article 1 did not report $\eta^{2}$ values but had the largest pairwise effects and *F*-statistics of the five articles in question. Article 3 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance, respectively. Similarly, variance explained on the self-efficacy measure was $\eta^{2}$ = .995, $\eta^{2}$ = .994, $\eta^{2}$ = .997 for the Time, Group, and Time x Group effects, respectively. Article 4 also reported $\eta^{2}$ = .99 for all three effects on both response time and response accuracy measures.

Article 5 reported $\eta^{2}$ = 1.0 for the main effect of Time and the Time x Group interaction, as well as $\eta^{2}$ = .95 for the main effect of Group on the response time measure. Interestingly, the Time x Group interaction had the smallest reported significant *F*-statistic among the five articles in question. With respect to response accuracy, the reported effects were $\eta^{2}$ = .98, $\eta^{2}$ = .94, $\eta^{2}$ = .93 for the Time, Group, and Time x Group analyses, respectively. Article 5 reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses, respectively.

@@

Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 4, 5, and 6. The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4). Articles 1, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 4, and 80 in Article 3. Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \@ref(tab:table1)). We assumed that each article was based on different samples as none of the articles mentioned using any previously published data.

Article 2 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online 11 days before we posted the first preprint of this paper (published September 3rd, 2021; preprint posted September 14th, 2021). We were unaware of Article 2 when posting the original preprint and it was not included in that version. However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes. Further, in comparing the reaction time and accuracy means and standard deviations reported in @lola2021b to those reported in @lola2021, it appeared the data shared a remarkably similar pattern. To investigate this similarity further, we conducted a correlation analysis between the two data sets. To do so, we created a vector of data for each article: Row 1 contained the pretest reaction time mean for the analogy group, row 2 the pretest reaction time standard deviation for the analogy group, and so on listing the means and standard deviations for the four groups and four time points on the two measures. Our analysis revealed the two data sets were highly correlated, *r* = .994.
